---
title: "Reading from the Web"
author: "Chhiring Lama"
date: "2024-10-10"
output: html_document
---


```{r, message = FALSE, echo = FALSE}
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Extracting Tables
```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_html = read_html(url)

drug_use_html
```

Get the pieces we need:
```{r}
marj_use_df <-drug_use_html |> 
  html_table() |> 
  first() |> 
  slice(-1)

knitr::kable(head(marj_use_df))
```


## Learning Assessment 
Create a data frame that contains the cost of living table for New York from [this page](https://www.bestplaces.net/cost_of_living/city/new_york/new_york).

### Solution:
```{r}
url2 = "https://www.bestplaces.net/cost_of_living/city/new_york/new_york"

bestplaces_nyc <- read_html(url2) |> 
  html_table( header = TRUE) |> 
  first() 

knitr::kable(bestplaces_nyc)

```

## CSS Selectors

```{r}
swm_html <- read_html("https://www.imdb.com/list/ls070150896/")
swm_html
```

```{r}
title_vec <- swm_html |> 
  html_elements(".ipc-title-link-wrapper .ipc-title__text") |> 
  html_text()

metascore_vec = 
  swm_html |>
  html_elements(".metacritic-score-box") |>
  html_text()

runtime_vec <- swm_html |>
  html_elements(".dli-title-metadata-item:nth-child(2)") |>
  html_text()

swm_df <- tibble(
    title = title_vec,
    score = metascore_vec,
    runtime = runtime_vec)
  
```

## Learning Assessment: 
[This page](https://books.toscrape.com/) contains some (made up) books. Use a process similar to the one above to extract the book titles, stars, and prices.

### Solution:
```{r}
url <- "https://books.toscrape.com/"

book_html <- read_html("https://books.toscrape.com/")

title_books <- book_html |> 
  html_elements("h3") |>
  html_text2()

book_stars <- book_html |> 
  html_elements(".star-rating") |> 
  html_attr("class")

book_prices <- book_html |> 
  html_elements(".price_color")|> 
  html_text()

books_df <- tibble(
  title = title_books, 
  rating = book_stars, 
  price = book_prices)
  
```

## Using API

```{r}
nyc_water <- GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") |> 
  content()
```

APIs where there is limit on number of rows
```{r}
prfss_df <- GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv", 
                query = list("$limit" = 5000)) |> 
  content()
```

## Pokemon API
```{r}
pokemon_df <- GET("https://pokeapi.co/api/v2/pokemon/ditto") |> 
  content()
```

```{r}
pokemon_df[["abilities"]]
pokemon_df[["moves"]]
```




